---
title: "Modeling"
author: "Bennour Mohamed Hsin"
date: "10 January 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
#library(caret)
#library(electoral)
```

I will upload all the data sets from my github repository into this work environment. The same date exist in my local machine, reproducibility is not going to be my priority (for now).

```{r}
path <- "~/Projects/elections/final_data"
files <- list.files(path,full.names = T) %>% as.list()
names <- list.files(path)

data <- lapply(files, read_csv)
  
```


```{r}
# create names vector of the constituances
vec_clean_names <- names %>% 
  str_remove(".csv")
list_clean_names <- vec_clean_names %>% as.list()

# assign the names to the list of data
names(data) <- vec_clean_names
```

I believe I should remove all the rows that contain the sums of columns, 

```{r}
damdam <- function(x){
  if(x[nrow(x),ncol(x)-1] == sum(x[nrow(x), ncol(x)-1])){
    x <- x[-nrow(x),]
  }
}

data_1 <- lapply(data, damdam)

new_path <- "~/Projects/elections/super_final_data/"
paste(new_path, list_clean_names[[1]], ".csv", sep = "")

for(i in 1:27){
  data_1[[i]] %>%
    write_csv(paste(new_path, list_clean_names[[i]], ".csv", sep = ""))
}
``` 


```{r}
#number of seats for each constituance
s <- c(8,6,10,9,7,7,8,9,8,5,7,6,8,9,9,7,6,7,9,8,6,10,4,4,9,8,5) 
```


```{r}
# sum all votes for each list in each constituance
hor_wize <- function(x){
  l <- ncol(x)
  x %>% 
    mutate(list_total = rowSums(x[,-l])) %>%
    select(list_total, list) %>%
    return()
}

sumlist <- lapply(data_1, hor_wize) %>% lapply(., as_tibble)
names(sumlist) <- vec_clean_names
```

```{r}
total <- lapply(sumlist, select, "list_total") %>% lapply(., pull)  

parties_num <- vector('list', 27) 
names(parties_num) <- vec_clean_names
num <- lapply(total, length)

for(i in 1:27){
  parties_num[[i]] <-  tibble(list_number = c(1:num[[i]])) %>%
    mutate(list_number = as.character(list_number))
}

lists <- lapply(sumlist, select, "list") %>% map2(., parties_num, bind_cols) 
```

I probably should store the list in seperate vectors each, than loop on these vectors names and do the calculations than store them to a list.


```{r}
library(electoral)
```

```{r}
funk <- function(){
  v <- vector("list",27)
  names(v) <- vec_clean_names
  for(i in 1:27){
    v[[i]] <- seats_lr(parties = parties_num[[i]], votes = total[[i]], n_seats = s[i], method = 'hare') %>% 
      enframe(name = NULL) %>%
      rowid_to_column() %>%
      filter(value > 0)
  }
  return(v)
}

results <- funk()

```


```{r}

fnac <- function(l, r){
  l %>%
    filter(list_number %in% r %>% select(rowid)) %>%
    return()
}

res_2 <- vector("list", 27)



```

the main lists I work with now are 

```{r}
results
lists
```

```{r}
ahla <- function(l, x){
  l %>%
    filter(list_number %in% x$rowid) %>%
    select(-list_number) %>%
    return()
}

seated_lists <- map2(lists, results, ahla)

sapply(results, nrow)
sapply(seated_lists, nrow)
```

```{r}
results[[4]] %>%
 bind_cols(seated_lists[[4]])
```








